%_____________________________________________________________________________________________ 
% LATEX Template: Department of Comp/IT BTech Project Reports
% Abstract of Report
% Sun Mar 27 10:34:00 IST 2011
%_____________________________________________________________________________________________ 
\setstretch{1.5}
\begin{abstract}
%\addcontentsline{toc}{chapter}{Abstract}	% This makes sure abstract is included in contents.
Optical Character Recognition(OCR) is widely used across many products and services offered by the company. Text localization/segmentation and text recognition form most important parts of any optical character recognition pipeline. The present text segmentation techniques in place perform well for machine printed documents but are not as effective for documents with handwritten content. We are working on improving the deep learning models for text localisation/segmentation part of the pipeline. We so far have explored 2 network architectures based on the literature surveyed - ARU Net and CRAFT. ARU Net was originally designed to be used on historic documents while CRAFT was designed for localization generic "text in the wild" scenario. In the data prepartion and pre-processing step - we prepared training data consisting of a wide variety of documents. To improve the results, we introduced image augmentations and modified the networks under study as per our observations. We introduced some post processing techniques to get better end-to-end results for the pipeline. We are able to get good line-level segmentation using ARU Net combined with some post-processing. For CRAFT, with a fully supervised training setup, we have been able achieve good segmentation results for machine print documents but improvements are needed for certain subset of our data and especially so for handwritten ones. Further experiments with semi-supervise training of modified CRAFT-like are in progress to further address these shortcomings.
\newline
\textbf{Keywords:}
\newline
ARU Net - Attention Residual U-Net
\newline
CRAFT - Character Region Awareness for Text Detection
\end{abstract}

%_____________________________________________________________________________________________ 
